### 2021-08-10 Manuscript.Rmd
Suppressed computation of bootstrapping for future knits
Bootstrapped internal consistencies have been saved as "consistencies.rds" and can be imported to save time

  # Set a number for the bootstrapping procedures
  bootnum <- 300

@@

  load(here("data.Rda"))
```

@@

## Data analysis
We used `r cite_r("r_references.bib")` for all our analyses.
### Multiple mediation model
Items were reverse coded according to the scale manuals.
NFC and self-control were computed as the sum scores of the NCS and the SCS, respectively.
Reduced personal efficacy was computed using the sum of the MBI subscale, and reappraisal and suppression were computed using the sum of each ERQ subscale.
### Structural equation model
Items were reverse coded according to the scale manuals.
The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure following Grass et al. [-@Grass2019], a method that is used in SEM when only relations between but not within constructs are of interest.
Principal component analysis was used to determine the factor loadings of each NCS item onto the first component.
Then, the items were randomly divided into four parcels and the average item loading per parcel was computed.
This was repeated 10,000 times to find the parcelling choice with the smallest difference in average item loadings between parcels.
The latent factor MBI was computed using the three subscales as indicators.
For the demand-resource-ratios, we used three items from the work satisfaction scale each, without reverse coding them.
The latent factor DTH was indicated by items 4, 8, and 9, DTL by items 12, 26, and 27, and DRF by items 17, 22, and 24.
### Exploratory analysis
We preregistered two exploratory analyses.
Firstly, we repeated the SEM with the subscale reduced personal efficacy in place of the MBI score, since this subscale has shown higher correlations with NFC than the other subscales [@Grass2018; @Naderi2018].
And secondly, we included a Covid-19 burden score into the SEM, computed as the sum of the Covid-19 items.

@@

```{r consistency, echo=FALSE, message=FALSE, warning=FALSE}

>>>>

  # Set a number for the bootstrapping procedures
  bootnum <- 5000

@@

  load(here("data.Rda"))

  # Load the internal consistencies (bootstrapping has been suppressed to save time on knitting)
  load(here("consistencies.rds"))

@@

## Data analysis
We used `r cite_r("r_references.bib")` for all our analyses.

### *Multiple mediation model*
Items were reverse coded according to the scale manuals.
NFC and self-control were computed as the sum scores of the NCS and the SCS, respectively.
Reduced personal efficacy was computed using the sum of the MBI subscale, and reappraisal and suppression were computed using the sum of each ERQ subscale.

### *Structural equation model*
Items were reverse coded according to the scale manuals.
The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure following Grass et al. [-@Grass2019], a method that is used in SEM when only relations between but not within constructs are of interest.
Principal component analysis was used to determine the factor loadings of each NCS item onto the first component.
Then, the items were randomly divided into four parcels and the average item loading per parcel was computed.
This was repeated 10,000 times to find the parcelling choice with the smallest difference in average item loadings between parcels.
The latent factor MBI was computed using the three subscales as indicators.
For the demand-resource-ratios, we used three items from the work satisfaction scale each, without reverse coding them.
The latent factor DTH was indicated by items 4, 8, and 9, DTL by items 12, 26, and 27, and DRF by items 17, 22, and 24.

### *Exploratory analysis*
We preregistered two exploratory analyses.
Firstly, we repeated the SEM with the subscale reduced personal efficacy in place of the MBI score, since this subscale has shown higher correlations with NFC than the other subscales [@Grass2018; @Naderi2018].
And secondly, we included a Covid-19 burden score into the SEM, computed as the sum of the Covid-19 items.

@@

```{r consistency, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
